---
title: "Gov 50 Final Project"
author: "Tova Kaplan"
description: "My Final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

I am interested in exploring data related to hate crimes in the US. In particular, I am interested in investigating the question of what causes/correlates to rises in hate crimes. Do areas with more Jewish/Black/Muslim/LGBT/other marginalized groups have higher or lower rates of hate crimes? Does this relationship hold across all minority catagories, or are there differences? Are there more hate crimes in certain seasons? More around religious holidays, elections? 

## Milestone 2
FBI Hate Crime Statistics Dataset: https://cde.ucr.cjis.gov/LATEST/webapp/#/pages/downloads 

Research question: Does a rise in Anti-Jewish hate crimes correlate with a rise in all other hate crimes? 

Hypothesis: My hypothesis is that an increase in anti-Jewish hate crimes is positively correlated with an increase in all other hate crimes. Furthermore, I believe that I will find a strong positive correlation. This is because I think that the same underlying political and cultural currents could cause both an increase in Anti-jewish crimes and crimes against other minority groups such as African Americans, Muslims, and gay people. In addition, a rise in Anti-Jewish hate crimes could be caused by an overall increase in crime, which would also cause all other hate crimes to rise. 

Explanatory variables: Anti-Jewish Hate Crimes
The outcome variable, in this case, would be "All Other Hate Crimes" or simply "Other Hate Crimes." The goal is to assess whether changes in the levels of Anti-Jewish hate crimes are associated with changes in the levels of all other hate crimes.


Observed pattern: The observed pattern that would provide support for my hypothesis would be if I perform a correlation analysis and discover a correlation coefficient above 0. 



```{r}
library(tidyverse)
```
```{r}
hate_crime <- read.csv("~/Downloads/hate_crime (1) 2/hate_crime/hate_crime.csv")
```


## Milestone 3

```{r}
anti_jewish_hate_crimes <- hate_crime %>%
  filter(bias_desc == "Anti-Jewish")

summary_data <- anti_jewish_hate_crimes %>%
  group_by(data_year, region_name) %>%
  summarise(count = n())

ggplot(data = summary_data, aes(x = data_year, y = count, fill = region_name, color = region_name)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_line(size = 1) +
  labs(title = "Anti-Jewish Hate Crimes Year-to-Year by Region",
       x = "Year",
       y = "Number of Hate Crimes") +
  scale_fill_brewer(palette = "Set1") +
  scale_color_brewer(palette = "Set1") +
  labs(fill = "Region:", color = "Region:") +  
  theme_minimal() 
```
## Milestone 4

```{r}
hate_crime_subset <- hate_crime %>%
  mutate(group = ifelse(bias_desc == "Anti-Jewish", "Anti-Jewish", "Other Hate Crimes")) %>%
  group_by(data_year, group) %>%
  summarise(count = n()) %>%
  ungroup()


hate_crime_pivot <- hate_crime_subset %>%
  pivot_wider(names_from = group, values_from = count, values_fill = 0)


correlation <- cor(hate_crime_pivot[, -1], method = "pearson")[1, 2]


ggplot(hate_crime_subset, aes(x = data_year, y = count, color = group)) +
  geom_line() +
  labs(title = "Trends in Anti-Jewish and Other Hate Crimes Over Time",
       x = "Year",
       y = "Number of Hate Crimes",
       color = "Hate Crime Type") +
  theme_minimal()

cat("Correlation between Anti-Jewish and Other Hate Crimes:", correlation, "\n")
```
```{r}
correlation <- cor(hate_crime_pivot[, -1], method = "pearson")[1, 2]

cat("Correlation between Anti-Jewish and Other Hate Crimes:", correlation, "\n")
```

```{r}
cor_hatecrimes <- cor(hate_crime$anti_jewish_hate_crimes, hate_crime$rr_lag, use = "pairwise")
cor_hatecrimes
```


The correlation found between Anti-Jewish and all other hate crimes is 0.465, which indicates a moderately strong positive correlation. 




```{r}
library(dplyr)
library(tidyr)

hate_crime_subset <- hate_crime %>%
  mutate(group = ifelse(bias_desc == "Anti-Jewish", "Anti-Jewish", "Other Hate Crimes")) %>%
  group_by(data_year, group) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = group, values_from = count, values_fill = 0) %>%
  ungroup() %>%
  mutate(total_count = rowSums(select(., starts_with("Anti-Jewish"))))

# View the resulting data frame
print(hate_crime_subset)
```
```{r}
library(dplyr)
library(tidyr)

hate_crime_subset <- hate_crime %>%
  group_by(data_year) %>%
  summarise(anti_jewish_count = sum(bias_desc == "Anti-Jewish"),
            total_count = n())

# View the resulting data frame
print(hate_crime_subset)
```
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

hate_crime_subset <- hate_crime %>%
  group_by(data_year) %>%
  summarise(anti_jewish_count = sum(bias_desc == "Anti-Jewish"),
            total_count = n())

correlation <- cor(hate_crime_subset[, -1], method = "pearson")[1, 2]

ggplot(hate_crime_subset, aes(x = data_year)) +
  geom_line(aes(y = anti_jewish_count, color = "Anti-Jewish"), size = 1.5) +
  geom_line(aes(y = total_count, color = "Total Hate Crimes"), size = 1.5) +
  labs(title = "Trends in Anti-Jewish and Total Hate Crimes Over Time",
       x = "Year",
       y = "Number of Hate Crimes",
       color = "Hate Crime Type") +
  theme_minimal()

cat("Correlation between Anti-Jewish and Total Hate Crimes:", correlation, "\n")
```
```{r}
hate_crime_subset <- hate_crime %>%
  group_by(data_year) %>%
  summarise(anti_jewish_count = sum(bias_desc == "Anti-Jewish"),
            total_count = n()) %>%
  mutate(percent_anti_jewish = (anti_jewish_count / total_count) * 100)

correlation <- cor(hate_crime_subset[, c("anti_jewish_count", "total_count")], method = "pearson")[1, 2]

# Fit linear model
lm_model <- lm(percent_anti_jewish ~ data_year, data = hate_crime_subset)

# Get coefficients of the model
coefficients <- coef(lm_model)

# Create equation text
equation_text <- paste0("y = ", round(coefficients[1], 2), " + ", round(coefficients[2], 2), " * x")

# Create the ggplot chart with regression equation
ggplot(hate_crime_subset, aes(x = data_year, y = percent_anti_jewish)) +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed", formula = y ~ x) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed", formula = y ~ x) +
  geom_text(aes(label = equation_text), x = max(hate_crime_subset$data_year), y = max(hate_crime_subset$percent_anti_jewish), hjust = 1, vjust = 1) +
  labs(title = "Proportion of Anti-Jewish Hate Crimes Through Time",
       x = "Year",
       y = "Percentage of Hate Crimes that are Anti-Jewish (%)",
       color = "Hate Crime Type") +
  theme_minimal()

# Print correlation and coefficients
cat("Correlation between Anti-Jewish and Total Hate Crimes:", correlation, "\n")
cat("Regression Equation:", equation_text, "\n")
```





```{r}
library(dplyr)
library(ggplot2)

regions <- unique(hate_crime$region_name)

plots <- list()

for (reg in regions) {
  # Exclude "Other" and "U.S. Territories"
  if (reg %in% c("Other", "U.S. Territories")) {
    next
  }

  subset_data <- hate_crime %>%
    filter(region_name == reg) %>%
    group_by(data_year) %>%
    summarise(anti_jewish_count = sum(bias_desc == "Anti-Jewish"),
              total_count = n()) %>%
    mutate(percent_anti_jewish = (anti_jewish_count / total_count) * 100)

  correlation <- cor(subset_data[, c("anti_jewish_count", "total_count")], method = "pearson")[1, 2]

  lm_model <- lm(percent_anti_jewish ~ data_year, data = subset_data)
  intercept <- coef(lm_model)[1]
  slope <- coef(lm_model)[2]

  equation_text <- sprintf("y = %.2f x + %.2f", slope, intercept)

  plot <- ggplot(subset_data, aes(x = data_year, y = percent_anti_jewish)) +
    geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed", formula = y ~ x) +
    geom_point() +
    labs(title = paste("Percentage of Anti-Jewish Hate Crimes in", reg),
         x = "Year",
         y = "Percentage of Anti-Jewish Hate Crimes",
         subtitle = equation_text) +
    theme_minimal()

  plots[[reg]] <- plot

  cat("Regression equation for Anti-Jewish and Total Hate Crimes in", reg, ":", equation_text, "\n")
}

# Display the plots
for (i in seq_along(plots)) {
  print(plots[[i]])
}
```







```{r}
# Assuming hate_crime includes a 'region_name' column
# Replace 'region_name' with the actual column name in your dataset
regions <- unique(hate_crime$region_name)

# Create an empty data frame to store the results
result_df <- data.frame()

# Perform linear regression on the entire dataset
total_data <- hate_crime %>%
  group_by(data_year) %>%
  summarise(anti_jewish_count = sum(bias_desc == "Anti-Jewish"),
            total_count = n()) %>%
  mutate(percent_anti_jewish = (anti_jewish_count / total_count) * 100)

total_lm_model <- lm(percent_anti_jewish ~ data_year, data = total_data)

# Summary of the linear model
total_summary_model <- summary(total_lm_model)

# Extract R-squared value for the total model
total_r_squared <- total_summary_model$r.squared

# Calculate residuals for the total model
total_residuals <- residuals(total_lm_model)

# Calculate standard deviation of residuals for the total model
total_std_dev <- sd(total_residuals)

# Create a data frame for the total model
total_result <- data.frame(
  Region = "All Regions Combined",
  Coefficient = coef(total_lm_model),
  P_Value = total_summary_model$coefficients[, 4],
  R_Squared = total_r_squared,
  Standard_Deviation = total_std_dev
)

# Append the total result to the main data frame
result_df <- bind_rows(result_df, total_result)

# Continue with the loop for individual regions
for (reg in regions) {
  # Exclude "U.S. Territories" and "Other"
  if (reg %in% c("U.S. Territories", "Other")) {
    next
  }

  subset_data <- hate_crime %>%
    filter(region_name == reg) %>%
    group_by(data_year) %>%
    summarise(anti_jewish_count = sum(bias_desc == "Anti-Jewish"),
              total_count = n()) %>%
    mutate(percent_anti_jewish = (anti_jewish_count / total_count) * 100)

  lm_model <- lm(percent_anti_jewish ~ data_year, data = subset_data)

  # Summary of the linear model
  summary_model <- summary(lm_model)

  # Extract R-squared value
  r_squared <- summary_model$r.squared

  # Calculate residuals for the model
  residuals_model <- residuals(lm_model)

  # Calculate standard deviation of residuals for the model
  std_dev_model <- sd(residuals_model)

  # Create a data frame with coefficients, p-values, R-squared, and standard deviation
  result <- data.frame(
    Region = reg,
    Coefficient = coef(lm_model),
    P_Value = summary_model$coefficients[, 4],
    R_Squared = r_squared,
    Standard_Deviation = std_dev_model
  )

  # Append the result to the main data frame
  result_df <- bind_rows(result_df, result)
}

# Add title to the top of the kable table
kable(result_df, format = "html", col.names = c("Region", "Coefficient", "P-Value", "R-Squared", "Standard Deviation")) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, position = "center") %>%
  add_header_above(c(" ", "Regression Information by Region" = 5))
```


